---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,        # Hide code output by default
  warning = FALSE,     # Suppress warnings in the output
  message = FALSE,     # Suppress messages in the output
  error = FALSE)      

library(dplyr)
library(ggplot2)
library(TeslaInvestR)

# Load data directly from the package
tesla_stock_filtered <- TeslaInvestR::filtered_tesla_stock
roadster_value_filtered <- TeslaInvestR::filtered_roadster_value
```

# TeslaInvestR

## Overview

**TeslaInvestR** is an R package designed for analyzing Tesla investment data. It provides users with access to historical Tesla stock price data and Tesla Roadster depreciation data, enabling direct comparisons between stock investment growth and vehicle depreciation. The package includes easy-to-use functions for financial analysis, interactive data visualization with `ggplot2`, and a user-friendly Shiny app.

## Key Features

- **Tesla Stock Data**: Access Tesla stock price data from 2011 to 2023, including adjusted close prices and computed investment values based on an initial investment.

- **Tesla Roadster Depreciation Data**: View simulated annual depreciation values for Tesla Roadsters from 2010 to 2024.

- **Interactive Visualization**: Use the Shiny app to explore and compare Tesla stock and Roadster depreciation trends in real time, including adjustable date ranges and investment type filtering.

- **Analysis Tools**: Built-in functions for filtering data by date, calculating investment growth, and visualizing both stock and depreciation data.

## Installation

Install the **TeslaInvestR** package directly from GitHub:

```{r}
# Install TeslaInvestR from GitHub
remotes::install_github("ETC5523-2024/assignment-4-packages-and-shiny-apps-nnam0004")
```

## Usage

### 1. Launching the Shiny App

Run the Shiny app to interactively explore Tesla investment data:

```{r eval=FALSE}
library(TeslaInvestR)
launch_shiny_app()
```

### 2. Comparing Stock and Depreciation Data with ggplot2

```{r}
# Add identifier columns
tesla_stock_filtered <- tesla_stock_filtered %>%
  dplyr::mutate(type = "Tesla Stock")

roadster_value_filtered <- roadster_value_filtered %>%
  dplyr::mutate(type = "Tesla Roadster")

# Combine datasets for plotting
combined_data <- bind_rows(
  tesla_stock_filtered %>% dplyr::select(Date, investment_value, type),
  roadster_value_filtered %>% dplyr::rename(Date = date) %>% dplyr::select(Date, investment_value, type)
)
```

## Data Sources

- **Tesla Stock Data**: Sourced from Yahoo Finance, covering the period from 2011 to 2023.
- **Tesla Roadster Depreciation Data**: Simulated data representing yearly depreciation of Tesla Roadsters from 2010 to 2024.

## License

This project is licensed under the MIT License. See the `LICENSE` file for details.

## Contributions

Contributions are welcome! Feel free to fork the repository, submit pull requests, or report issues to help improve the package.

## Documentation

For full documentation and tutorials, visit the pkgdown site here: [TeslaInvestR Documentation](https://etc5523-2024.github.io/assignment-4-packages-and-shiny-apps-nnam0004/).
