---
title: "Demonstrating the Use of TeslaInvestR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Demonstrating the Use of TeslaInvestR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
# Vignette setup chunk
library(dplyr)
library(ggplot2)

# Load data directly from the package
tesla_stock_filtered <- TeslaInvestR::filtered_tesla_stock
roadster_value_filtered <- TeslaInvestR::filtered_roadster_value
```

# Introduction

The `TeslaInvestR` package provides functions and data related to Tesla stock and Roadster depreciation. The package allows users to explore investment trends in Tesla stock as well as the depreciation of Tesla Roadsters.

## Package Installation

You can install the package from GitHub using:


## Working with Tesla Stock Data

The package contains the tesla_stock dataset, which provides historical data on Tesla stock prices. You can interact with this dataset as follows:

```{r}
head(tesla_stock_filtered)
```


## Example: Comparing Tesla Stock and Roadster Depreciation

You can compare the trends in Tesla stock price and Roadster depreciation by plotting them together using ggplot2:
```{r}

# Assuming tesla_stock and roadster_value are already loaded

# Add an identifier to each dataset
tesla_stock_filtered <- tesla_stock_filtered %>%
  dplyr::mutate(type = "Tesla Stock")

roadster_value_filtered <- roadster_value_filtered %>%
  dplyr::mutate(type = "Tesla Roadster")

# Combine the two datasets into one
combined_data <- bind_rows(
  tesla_stock_filtered %>% dplyr::select(Date, investment_value, type),
  roadster_value_filtered %>% dplyr::rename(Date = date) %>% dplyr::select(Date, investment_value, type)
)

# Plot with facets
ggplot2::ggplot(combined_data, aes(x = Date, y = investment_value, color = type)) +
  geom_line() +
  labs(title = "Comparison of Tesla Stock and Roadster Depreciation",
       x = "Date", y = "Value") +
  facet_wrap(~type, scales = "free_y") +  # Facet by the type (Tesla Stock and Tesla Roadster)
  theme_minimal()

```

## Conclusion

The TeslaInvestR package provides useful data and tools for analyzing the historical trends in Tesla stock and the depreciation of Tesla Roadsters.

