---
title: "Demonstrating the Use of TeslaInvestR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Demonstrating the Use of TeslaInvestR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,        # Hide code output by default
  warning = FALSE,     # Suppress warnings in the output
  message = FALSE,     # Suppress messages in the output
  error = FALSE)      
```

# Introduction

The `TeslaInvestR` package provides data and tools for analyzing Tesla's historical stock prices and the depreciation trends of Tesla Roadsters. The package includes preprocessed datasets and functions that enable users to visualize and explore these financial trends interactively.

In this vignette, we will demonstrate how to use `TeslaInvestR` for data exploration, analysis, and visualization of Tesla-related investments.

## Package Installation

To install `TeslaInvestR` from GitHub, use the following commands:

```{r eval=FALSE}
# Specify a CRAN mirror and install 'remotes'
install.packages("remotes", repos = "https://cloud.r-project.org/")
```

```{r eval=FALSE}
# Install TeslaInvestR
remotes::install_github("ETC5523-2024/assignment-4-packages-and-shiny-apps-nnam0004")

# Example of running the Shiny app
library(TeslaInvestR)

```

## Loading Data and Libraries

After installing the package, load the necessary libraries and the datasets provided by `TeslaInvestR`.

```{r echo=FALSE}
library(dplyr)
library(ggplot2)
library(TeslaInvestR)

# Load data directly from the package
tesla_stock_filtered <- TeslaInvestR::filtered_tesla_stock
roadster_value_filtered <- TeslaInvestR::filtered_roadster_value
```

## Exploring Tesla Stock Data

The `tesla_stock_filtered` dataset contains historical data on Tesla's stock prices. We can take a quick look at the structure of the dataset using `head()`.

```{r eval=FALSE}
head(tesla_stock_filtered)
```

### Data Description

- **Date**: The date of each observation.
- **Adj_Close**: Adjusted closing price of Tesla stock on that date.
- **investment_value**: Calculated investment value based on the adjusted closing price.

## Example: Comparing Tesla Stock Prices and Roadster Depreciation

The package includes a dataset on the depreciation values of Tesla Roadsters, allowing us to compare the stock's growth to the car's depreciation.

### Data Preparation

To create a comparison plot, we’ll:

1. Add an identifier for each dataset (`type` column).

2. Combine the `tesla_stock_filtered` and `roadster_value_filtered` datasets into one data frame.

```{r}
# Add identifier columns
tesla_stock_filtered <- tesla_stock_filtered %>%
  dplyr::mutate(type = "Tesla Stock")

roadster_value_filtered <- roadster_value_filtered %>%
  dplyr::mutate(type = "Tesla Roadster")

# Combine datasets for plotting
combined_data <- bind_rows(
  tesla_stock_filtered %>% dplyr::select(Date, investment_value, type),
  roadster_value_filtered %>% dplyr::rename(Date = date) %>% dplyr::select(Date, investment_value, type)
)
```

### Visualization: Tesla Stock vs. Roadster Depreciation

Using `ggplot2`, we can plot the investment value over time for both Tesla stock and Roadster depreciation. We'll use `facet_wrap` to separate the plots for easier comparison.

```{r}
ggplot2::ggplot(combined_data, aes(x = Date, y = investment_value, color = type)) +
  geom_line(size = 1) +
  labs(
    title = "Comparison of Tesla Stock and Roadster Depreciation Over Time",
    x = "Date", y = "Value (USD)"
  ) +
  facet_wrap(~type, scales = "free_y") +  # Separate plots for stock and roadster
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    legend.position = "none"
  )
```

### Interpretation of the Plot

- **Tesla Stock**: The stock plot illustrates the upward trend in Tesla’s stock price over time, reflecting growth in Tesla's market value.
- **Tesla Roadster**: The Roadster depreciation plot shows a downward trend, typical of vehicle depreciation over time.

This side-by-side visualization provides an intuitive comparison of how Tesla stock has appreciated while the Roadster has depreciated.

## Conclusion

The `TeslaInvestR` package provides preprocessed datasets and functions that allow for easy exploration and visualization of Tesla's stock performance and the depreciation of Tesla Roadsters. This vignette demonstrated how to load the data, prepare it for analysis, and visualize these trends using `ggplot2`.

By using `TeslaInvestR`, users can quickly gain insights into Tesla's investment trends and make comparisons between stock and vehicle depreciation.
